title: 'HTE Test GRF'
date: "École Polytechnique - Autumn 2019"
output:
  html_document:
    df_print: paged
  pdf_document:
    citation_package: natbib
    includes:
      in_header: ../preamble.sty
    number_sections: yes
fontsize: 11pt
geometry: left=1.45in,top=1.35in,right=1.45in,bottom=1.35in
lang: en
linkcolor: red
classoption: a4paper
citecolor: green
urlcolor: blue
---
```{r, message=FALSE}
library(grf)
library(caret)
library(missForest)
library(doParallel)
library(missMDA)
library(ggplot2)
library(doParallel)
library(missMDA)
library(fBasics)     
library(corrplot)    



library(DiagrammeR)
library(DiagrammeRsvg)

registerDoParallel()

```





We now load the data and fill the missing values using MissForest
```{r, message=FALSE}
setwd("PATH TO WORK DIR")
rawData <- read.csv("data_preprocessed_2.csv",   na.strings = c("", "NR", "NA", "NF","IMP", "ND"),sep = ",")


# We filter out non lesions, which are patients for which we assignd cluster -1 in the python Notebook
rawData <- rawData[rawData$cluster != -1 ,]

# We extract Y and W
Y = rawData$Death
W = rawData$Tranexamic.acid


# We fill the missing values
rawData <- missForest(rawData, verbose = TRUE, parallelize = 'variables') 
```

Let's save the result for further use
```{r, message=FALSE}
write.csv(rawData$ximp, file = "data_preprocessed_missForest.csv")
```

Let's do some simple preprocessing and train our first causal forest
```{r}
X <- read.csv("data_preprocessed_missForest.csv")
X$X.1 <- NULL
X$Unnamed..0 <- NULL
X$X <- NULL

Y = X$Death
W = X$Tranexamic.acid

# We remove useless columns as not to to create biais in our statistical analysis (this holds mostly for causal forests)
X$Death <- NULL
X$Tranexamic.acid<- NULL

# We trin our causal forest
tau.forest <- causal_forest(X, Y, W, num.trees = 2000)
average_treatment_effect(tau.forest, method="AIPW", target.sample = "all")

```


We can generate basic statistics about the dataset

```{r}
summ_stats <- fBasics::basicStats(X)
summ_stats <- as.data.frame(t(summ_stats))

# Rename some of the columns for convenience
summ_stats <- summ_stats[c("Mean", "Stdev", "Minimum", "1. Quartile", "Median",  "3. Quartile", "Maximum")]
colnames(summ_stats)[colnames(summ_stats) %in% c('1. Quartile', '3. Quartile')] <- c('Lower quartile', 'Upper quartile')
```

```{r}
summ_stats
```

We can also compute a correlation matrix

```{r}
png(height=1500, width=1500, pointsize=15, file="overlap_simplified.png")
M <- cor(X)
corrplot(M, method = "circle", type="upper")
```

Some simple plots : 

```{r}
dat <- data.frame(table(W,Y))
names(dat) <- c("W","Y","Count")

ggplot(data=dat, aes(x=W, y=Count, fill=Y)) + geom_bar(stat="identity")
```
```{r}
dat <- data.frame(table(X$cluster,W))
names(dat) <- c("cluster","W","Count")

ggplot(data=dat, aes(x=cluster, y=Count, fill=W)) + geom_bar(stat="identity")
```

```{r}
dat <- data.frame(table(X$grade  ,W))
names(dat) <- c("grade","W","Count")

ggplot(data=dat, aes(x=grade, y=Count, fill=W)) + geom_bar(stat="identity")
```


```{r}
dat <- data.frame(table(X$grade  ,Y))
names(dat) <- c("grade","Y","Count")

ggplot(data=dat, aes(x=grade, y=Count, fill=Y)) + geom_bar(stat="identity")
```

# Causal forests

We might want to look at the important parameters in forest splits

```{r}
var_imp <- c(variable_importance(tau.forest))
names(var_imp) <- colnames(X_dummy)
sorted_var_imp <- sort(var_imp, decreasing=TRUE)

sorted_var_imp
```

To see what a single tree looks like 

```{r}
tree.plot = plot(get_tree(tau.forest, 1))
cat(DiagrammeRsvg::export_svg(tree.plot), file='plot_simplified.svg')
```


To plot the prediction histogram 

```{r, message=FALSE}
tau.hat.oob <- predict(tau.forest)
hist(tau.hat.oob$predictions)
```



Estimate the conditional average treatment effect on the full sample (CATE) for treated patients
```{r, message=FALSE}
average_treatment_effect(tau.forest, target.sample = "treated")
```

```{r}
print("Importance : Low")
average_treatment_effect(tau.forest, subset = (X_dummy$grade == 0), method="AIPW", target.sample = "overlap")
print("")
print("Importance : High")
average_treatment_effect(tau.forest, subset = (X_dummy$grade == 1), method="AIPW", target.sample = "overlap")
```


```{r}
average_treatment_effect(tau.forest, method = "AIPW", target.sample = "all")
```



New.csv is the original completed dataset with aditionnal columns containing the clusters numbers, they are generated by the python file "hierarchical_clustering.py"

```{r}
new <- read.csv("new.csv")
```

We can plot the ATE for each cluster

```{r}
for (val in c(0:19))
{
   print(average_treatment_effect(tau.forest, target.sample = "all", method="AIPW", subset = (new$X20_clusters == val)))
}

```

